HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-09-23 paper/main.tex
minor corrections, vectored diagram

\documentclass[11pt,letterpaper]{article}
%\usepackage[round]{natbib}
\usepackage{acl2016}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{pgfplotstable}
\usepackage{titlesec}
\usepackage{color}
\usepackage{lipsum,adjustbox}
\usepackage[font={small}]{caption}
%\usepackage{hyperref}

@@

Human judgement is the cornerstone for estimating the quality of an MT system.
Nevertheless, common measures for human MT evaluation, such as adequacy and fluency judgements
or the relative ranking of possible translations, are problematic in two ways.
First, as the quality of translation is multi-faceted, it is difficult
to quantify the quality of the entire sentence in a single number. This
is indeed reflected in the diminishing inter-annotator agreement (IAA) rates of human ranking measures
with the sentence length \cite{Bojar:2011}.
Second, a sentence-level quality score does not indicate what parts of the sentence
are badly translated, and so cannot inform developers in repairing these errors.

@@

We propose the HUME metric,
a human evaluation measure that decomposes over the UCCA semantic units.
% of the sentence.
UCCA \parcite{abend2013universal} is an appealing candidate for semantic analysis,
due to its cross-linguistic applicability, support for rapid annotation, and coverage
of many fundamental semantic phenomena, such as verbal, nominal and adjectival
argument structures and their inter-relations.

@@

\paragraph{MT Evaluation.}
%MT evaluation has been traditionally pursued through human-based
%evaluation that quantifies the adequacy of the translation in preserving the meaning 
%of the source sentence, and its fluency as a sentence in the target language
%\parcite{lopez2008statistical}.
Human evaluation is generally done by ranking the outputs of multiple systems
e.g., in the WMT tasks \parcite{bojar2015findings}, or by assigning
adequacy/fluency scores to each translation, a procedure recently improved
by \perscite{graham2015accurate} under the title Direct Assessment. We use this method to compare and contrast
with HUME later in the paper. HTER~\parcite{snover2006study} is another widely used human evaluation metric
which uses edit distance metrics to compare a translation and its human 
post-edition. HTER suffers from the problem that small edits in the translation
could in fact be serious flaws in accuracy, e.g., deleting a negation. 
Some manual measures ask annotators to explicitly mark errors, but this has
been found to have even lower agreement than ranking \parcite{lommel:etal:mqm-iaa:2014}.

@@

\begin{figure*}[t]
\begin{tabular}{c}
\includegraphics[width=1\textwidth]{tree_653_ver2.png}\\
%\includegraphics[width=0.6\textwidth]{DAline-extract.png}
\end{tabular}
\caption{An example of a doubly annotated HUME en-de sentence. The color of the nodes correspond to their
  HUME label: yellow (A), blue (B), and atomic nodes with their traffic. Nodes in which the annotators
  disagree are split in color. The scale at the bottom right shows a sample of 10 raw DA assessments
  for this example. }
\label{fig:humeeg}
\end{figure*}
%Original sentence ID = 653
%HUME SID=287
%RAW DA
%82.0+36.0+57.0+32.0+74.0+57.0+24.0+95.0+30.0+0.0+70.0+38.0+41.0+92.0+45.0+15.0+59.0+82.0+24.0+87.0+24.0+24.0+86.0+87.0+8.0+36.0+43.0+61.0+41.0+14.0+0.0+15.0+50.0+16.0+26.0+23.0+83.0+39.0+45.0+1.0+80.0+31.0+53.0+12.0+64.0+22.0+46.0+39.0
%STD DA
%-0.345604136518,-3.33742540772,0.423428930981,-0.548184035933,-0.677176346874,-1.65622648693,-1.55926607798,-1.1272965301,-0.0171653191891,-1.02340816821,-0.872524664699,-0.966670725408,-0.280564543666,-3.14230662916,-0.0830045886964,-1.47697478054,0.470426332641,-1.1678743283,-0.432290259946,-1.92671695959,0.141372817859,-1.36373703007,-0.179200976557,-0.427598369803
%
%54.8 = sample of 10 raw scores
%-0.230 = sample of 10 std scores
%Generate a random sample each time: here is one random sample from score_segs.R: 
%57+64+0+39+83+50+45+53+32+46
%57+64+0+39+83+50+45+53+32+46
%36+64+80+41+1+83+46+50+39+95=535 -> show this one as is closest to 54.8

@@

%While a quantitative comparison between DA and HUME, as we have just presented, is telling of their
%differences and commonalities, it is important to note that the two measures are fundamentally different.
Figure~\ref{fig:humeeg} presents an example of a doubly HUME-annotated English-German example
accompanied by 10 raw DA scores assigned to that sentence.
The figure illustrates the conceptual difference between the measures:
while DA standardises and averages scores across annotators to denoise the
crowd-sourced raw data, thus obtaining a single aggregate score,
HUME decomposes over a combinatorial structure, thus allowing to
localize the translation errors. We turn to comparing HUME to a more
conceptually-related  measure, namely HMEANT.

@@

\section*{Acknowledgments}
{T}his work was conducted within the scope of the \ProjectType, which has received funding from the European Union's Horizon 2020 research and innovation programme under grant agreement No \GrantNo\ (\ProjectName).

>>>>

\documentclass[11pt,letterpaper]{article}
%\usepackage[round]{natbib}
\usepackage{acl2016}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\usepackage{url}
\usepackage{pgfplotstable}
\usepackage{titlesec}
\usepackage{color}
\usepackage{lipsum,adjustbox}
\usepackage[font={small}]{caption}
%\usepackage{hyperref}
\usetikzlibrary{positioning}

@@

%Human judgement is the cornerstone for estimating the quality of an MT system.
Human judgement should be the ultimate test of the quality of an MT system.
Nevertheless, common measures for human MT evaluation, such as adequacy and fluency judgements
or the relative ranking of possible translations, are problematic in two ways.
First, as the quality of translation is multi-faceted, it is difficult
to quantify the quality of the entire sentence in a single number. This
is indeed reflected in the diminishing inter-annotator agreement (IAA) rates of human ranking measures
with the sentence length \cite{Bojar:2011}.
Second, a sentence-level quality score does not indicate what parts of the sentence
are badly translated, and so cannot inform developers in repairing these errors.

@@

We propose the HUME metric,
a human evaluation measure that decomposes over UCCA semantic units.
% of the sentence.
UCCA \parcite{abend2013universal} is an appealing candidate for semantic analysis,
due to its cross-linguistic applicability, support for rapid annotation, and coverage
of many fundamental semantic phenomena, such as verbal, nominal and adjectival
argument structures and their inter-relations.

@@

\paragraph{MT Evaluation.}
%MT evaluation has been traditionally pursued through human-based
%evaluation that quantifies the adequacy of the translation in preserving the meaning 
%of the source sentence, and its fluency as a sentence in the target language
%\parcite{lopez2008statistical}.
Human evaluation is generally done by ranking the outputs of multiple systems
e.g., in the WMT tasks \parcite{bojar2015findings}, or by assigning
adequacy/fluency scores to each translation, a procedure recently improved
by \perscite{graham2015accurate} under the title Direct Assessment. We use this latter method to compare and
contrast
with HUME later in the paper. HTER~\parcite{snover2006study} is another widely used human evaluation metric
which uses edit distance metrics to compare a translation and its human 
post-edition. HTER suffers from the problem that small edits in the translation
could in fact be serious flaws in accuracy, e.g., deleting a negation. 
Some manual measures ask annotators to explicitly mark errors, but this has
been found to have even lower agreement than ranking \parcite{lommel:etal:mqm-iaa:2014}.

@@

\begin{figure*}[t]
\begin{tikzpicture}
\node(tree) [] {\includegraphics[width=1\textwidth]{tree_653_de1_de2.pdf}};
\node [below right = -2cm and  -8cm of tree]{\includegraphics[width=0.4\textwidth]{DAline-extract.png}};
\end{tikzpicture}
%\begin{tabular}{c}
%\includegraphics[width=1\textwidth]{tree_653_ver2.png}\\
%\includegraphics[width=0.6\textwidth]{DAline-extract.png}
%\end{tabular}
\caption{An example of a doubly annotated HUME en-de sentence. The color of the nodes correspond to their
  HUME label: yellow (A), blue (B), and atomic nodes with their traffic. Nodes in which the annotators
  disagree are split in color. The scale at the bottom right shows a sample of 10 raw DA assessments
  for this example. }
\label{fig:humeeg}
\end{figure*}
%Original sentence ID = 653
%HUME SID=287
%RAW DA
%82.0+36.0+57.0+32.0+74.0+57.0+24.0+95.0+30.0+0.0+70.0+38.0+41.0+92.0+45.0+15.0+59.0+82.0+24.0+87.0+24.0+24.0+86.0+87.0+8.0+36.0+43.0+61.0+41.0+14.0+0.0+15.0+50.0+16.0+26.0+23.0+83.0+39.0+45.0+1.0+80.0+31.0+53.0+12.0+64.0+22.0+46.0+39.0
%STD DA
%-0.345604136518,-3.33742540772,0.423428930981,-0.548184035933,-0.677176346874,-1.65622648693,-1.55926607798,-1.1272965301,-0.0171653191891,-1.02340816821,-0.872524664699,-0.966670725408,-0.280564543666,-3.14230662916,-0.0830045886964,-1.47697478054,0.470426332641,-1.1678743283,-0.432290259946,-1.92671695959,0.141372817859,-1.36373703007,-0.179200976557,-0.427598369803
%
%54.8 = sample of 10 raw scores
%-0.230 = sample of 10 std scores
%Generate a random sample each time: here is one random sample from score_segs.R: 
%57+64+0+39+83+50+45+53+32+46
%57+64+0+39+83+50+45+53+32+46
%36+64+80+41+1+83+46+50+39+95=535 -> show this one as is closest to 54.8

@@

%While a quantitative comparison between DA and HUME, as we have just presented, is telling of their
%differences and commonalities, it is important to note that the two measures are fundamentally different.
Figure~\ref{fig:humeeg} presents an example of a doubly HUME-annotated English-German example
accompanied by 10 raw DA scores assigned to that sentence.
The figure illustrates the conceptual difference between the measures:
while DA standardises and averages scores across annotators to denoise the
crowd-sourced raw data, thus obtaining a single aggregate score,
HUME decomposes over a combinatorial structure, thus allowing to
localize the translation errors. We now turn to comparing HUME to a more
conceptually-related  measure, namely HMEANT.

@@

\section*{Acknowledgments}
%{T}his work was conducted within the scope of the \ProjectType, which has received funding from the European Union's Horizon 2020 research and innovation programme under grant agreement No \GrantNo\ (\ProjectName).

This project has received funding from the European Union's Horizon 2020 research and innovation
programme under grant agreement \GrantNo\ (\ProjectName).
